---
title: "<center> AFG MSNA 2020 </center>"

output: html_document
   
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE,comment = NA, message = FALSE, warning=FALSE, fig.align = 'center' )
```

<center> Data Collection Monitoring Report. Last updated: `r substr(Sys.time(), 0, 19)`

<!-- *** -->

```{r, include=FALSE}
library(knitr)
library(kableExtra)
library(lubridate)
library(tidyr)
library(gsubfn)
library(dplyr)
library(formattable)
library(readxl)
library(DT)
library(plotly)
library(stringr)
source("functions/audit_function.R")
`%notin%` <- Negate(`%in%`)

assessment_start_date <- as.Date("2020-08-08")
time_limit <- 29.5
max_interv <- 6

# import raw data
data <- read_excel("input/processed/msna_2020_processed_raw_data.xlsx")

# Sample
sample_df <- read_excel("input/sample/WoAA_2020_Compiled_Sample_20200721.xlsx")
sample_df <- sample_df %>% mutate(
  pop_group_final = case_when(
    pop_group == "recent_returnees" | pop_group == "non_recent_returnees" ~ "returnees",
    TRUE ~ pop_group
  ),
  prov_key = paste0(province_kobo,"_",pop_group_final),
  dist_key = paste0(district_kobo,"_",pop_group_final)
)
national_sample <- sample_df %>% group_by(pop_group) %>% summarise(
  Target = sum(survey_buffer, na.rm = T)
)
prov_sample <- sample_df %>% group_by(prov_key, province, pop_group_final) %>% summarise(
  Target = sum(survey_buffer, na.rm = T)
)


dist_sample <- read_excel("input/sample/dist_sample_updated.xlsx") %>% select(-c(Target_orginal)) %>% filter(Target != 0)

openxlsx::write.xlsx(dist_sample, "dist_sample.xlsx")


dist_sample_wrong_dist <- dist_sample %>% select(dist_key, pop_group_final,Target)

gender_sample <- read_excel("input/sample/gender_sample.xlsx")


data_tracking <- data %>% filter(interview_type == "hoh" | interview_number == "no" | is.na(interview_number))

## Tracking at National level ##### 

national_tracking <- data_tracking %>% 
  group_by(pop_group_national) %>% 
  summarise(Received = n(),
            Deleted = sum(validity == "deleted", na.rm = T),
            Accepted = sum(validity == "valid", na.rm = T)
  )

national_tracking_merged <- left_join(national_sample, national_tracking, by = c("pop_group"= "pop_group_national"))  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Target,
      TRUE ~ (Accepted - Target) * -1,
    ),
    Deletion_Rate = paste0(round((((Deleted / Received) * 100)), digits = 0 ), "%"),
    perc_complete = paste0(round((((Accepted / Target) * 100)), digits = 0 ), "%"),
    perc_complete = case_when(
      perc_complete == "NA%" ~ NA_character_,
      TRUE ~ perc_complete
    ),
    Deletion_Rate = case_when(
      Deletion_Rate == "NA%" ~ NA_character_,
      TRUE ~ Deletion_Rate
    )
    
  ) %>% mutate_all(
    funs(replace_na(.,0))) %>% ungroup()  %>% select(
      Population_Group = pop_group, Target, Received, Accepted, Deleted, Deletion_Rate, perc_complete, Remaining
    ) %>% mutate(
      Population_Group = case_when(
      Population_Group == "non_recent_idps" ~ "Non Recent IDPs",
      Population_Group == "recent_idps" ~ "Recent IDPs",
      Population_Group == "refugees" ~ "Refugees",
      Population_Group == "non_recent_returnees" ~ "Non Recent Returnees",
      Population_Group == "recent_returnees" ~ "Recent Returnees",
      Population_Group == "vulnerable" ~ "Vulnerable",
        
      TRUE ~ Population_Group
      )
    )

## Tracking by province ##### 

province_tracking <- data_tracking %>% 
  group_by(prov_key) %>% 
  summarise(Received = n(),
            Deleted = sum(validity == "deleted", na.rm = T),
            Accepted = sum(validity == "valid", na.rm = T)
  )

province_tracking_merged <- left_join(prov_sample, province_tracking, by = "prov_key")  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Target,
      TRUE ~ (Accepted - Target) * -1,
    ),
    Deletion_Rate = paste0(round((((Deleted / Received) * 100)), digits = 0 ), "%"),
    perc_complete = paste0(round((((Accepted / Target) * 100)), digits = 0 ), "%"),
    perc_complete = case_when(
      perc_complete == "NA%" ~ NA_character_,
      TRUE ~ perc_complete
    ),
    Deletion_Rate = case_when(
      Deletion_Rate == "NA%" ~ NA_character_,
      TRUE ~ Deletion_Rate
    )
    
  ) %>% mutate_all(
    funs(replace_na(.,0))) %>% ungroup()  %>% select(
      Province = province, Population_Group = pop_group_final, Target, Received, Accepted, Deleted, Deletion_Rate, perc_complete, Remaining
    ) %>% mutate(
      Population_Group = case_when(
      Population_Group == "non_recent_idps" ~ "Non Recent IDPs",
      Population_Group == "recent_idps" ~ "Recent IDPs",
      Population_Group == "refugees" ~ "Refugees",
      Population_Group == "returnees" ~ "Returnees",
      Population_Group == "vulnerable" ~ "Vulnerable",
      TRUE ~ Population_Group
      )
    )

province_tracking_merged$Province <-stringr::str_to_sentence(province_tracking_merged$Province)

## Tracking at district level ##### 

district_tracking <- data_tracking %>% 
  group_by(dist_key) %>% 
  summarise(Received = n(),
            Deleted = sum(validity == "deleted", na.rm = T),
            Accepted = sum(validity == "valid", na.rm = T)
  )

district_tracking_merged <- left_join(dist_sample, district_tracking, by = "dist_key")  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Target,
      TRUE ~ (Accepted - Target) * -1,
    ),
    Deletion_Rate = paste0(round((((Deleted / Received) * 100)), digits = 0 ), "%"),
    perc_complete = paste0(round((((Accepted / Target) * 100)), digits = 0 ), "%"),
    perc_complete = case_when(
      perc_complete == "NA%" ~ NA_character_,
      TRUE ~ perc_complete
    ),
    Deletion_Rate = case_when(
      Deletion_Rate == "NA%" ~ NA_character_,
      TRUE ~ Deletion_Rate
    )
    
  ) %>% mutate_all(
    funs(replace_na(.,0))) %>% ungroup()  %>% select(
      Province = province, District = district, Population_Group = pop_group_final, Target, Received, Accepted, Deleted, Deletion_Rate, perc_complete, Remaining
    ) %>% mutate(
      Population_Group = case_when(
      Population_Group == "non_recent_idps" ~ "Non Recent IDPs",
      Population_Group == "recent_idps" ~ "Recent IDPs",
      Population_Group == "refugees" ~ "Refugees",
      Population_Group == "returnees" ~ "Returnees",
      Population_Group == "vulnerable" ~ "Vulnerable",
      TRUE ~ Population_Group
      )
    ) %>% arrange(Province)

district_tracking_merged$Province <-stringr::str_to_sentence(district_tracking_merged$Province)


## Tracking Gender component
gender_tracking <- data %>% filter(interview_type == "non_hoh") %>% 
  group_by(province) %>% 
  summarise(Received = n(),
            Deleted = sum(validity == "deleted", na.rm = T),
            Accepted = sum(validity == "valid", na.rm = T)
  )

gendert_tracking_merged <- left_join(gender_sample, gender_tracking, by = "province")  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Target,
      TRUE ~ (Accepted - Target) * -1,
    ),
    Deletion_Rate = paste0(round((((Deleted / Received) * 100)), digits = 0 ), "%"),
    perc_complete = paste0(round((((Accepted / Target) * 100)), digits = 0 ), "%"),
    perc_complete = case_when(
      perc_complete == "NA%" ~ NA_character_,
      TRUE ~ perc_complete
    ),
    Deletion_Rate = case_when(
      Deletion_Rate == "NA%" ~ NA_character_,
      TRUE ~ Deletion_Rate
    )
    
  ) %>% mutate_all(
    funs(replace_na(.,0))) %>% ungroup()  %>% select(
      Province = province, Target, Received, Accepted, Deleted, Deletion_Rate, perc_complete, Remaining
    ) %>% arrange(Province)

gendert_tracking_merged$Province <-stringr::str_to_sentence(gendert_tracking_merged$Province)


## Tracking Wrong Population Group ##### 
district_wrong_pop <- data %>% 
  group_by(dist_key, province, district, pop_group = pop_group_final) %>% 
  summarise(Received = n(),
            Deleted = sum(validity == "deleted", na.rm = T),
            Accepted = sum(validity == "valid", na.rm = T)
  )

district_wrong_pop_merged <- left_join( district_wrong_pop, dist_sample_wrong_dist, by = "dist_key")  %>%
  mutate(
    Remaining =  case_when(
      is.na(Accepted) ~ Target,
      TRUE ~ (Accepted - Target) * -1,
    ),
    Deletion_Rate = paste0(round((((Deleted / Received) * 100)), digits = 0 ), "%"),
    perc_complete = paste0(round((((Accepted / Target) * 100)), digits = 0 ), "%"),
    perc_complete = case_when(
      perc_complete == "NA%" ~ NA_character_,
      TRUE ~ perc_complete
    ),
    Deletion_Rate = case_when(
      Deletion_Rate == "NA%" ~ NA_character_,
      TRUE ~ Deletion_Rate
    )
    
  ) %>% mutate_all(
    funs(replace_na(.,0))) %>% ungroup()  %>% select(
      Province = province, District = district, Population_Group = pop_group, Target, Received, Accepted, Deleted, Deletion_Rate, perc_complete, Remaining
    ) %>% mutate(
      Population_Group = case_when(
        Population_Group == "non_recent_idps" ~ "Non Recent IDPs",
        Population_Group == "recent_idps" ~ "Recent IDPs",
        Population_Group == "refugees" ~ "Refugees",
        Population_Group == "returnees" ~ "Returnees",
        Population_Group == "vulnerable" ~ "Vulnerable",
        TRUE ~ Population_Group
      )
    ) %>% arrange(Province) %>% filter(Target == 0)

district_wrong_pop_merged$Province <-stringr::str_to_sentence(district_wrong_pop_merged$Province)
district_wrong_pop_merged$District <-stringr::str_to_sentence(district_wrong_pop_merged$District)


# Overall progress General

Overall_progress <- district_tracking_merged %>%
  group_by(Province) %>%
  summarise(Target = sum(Target),
            Accepted = sum(Accepted, na.rm = T))


Overall_progress_prov_graphs <- Overall_progress %>%
  mutate(percentage =  round((Accepted / Target), digits = 3),
          percentage = case_when(
           percentage >= 1 ~ 1,
           TRUE ~ percentage
         ),
         group=ifelse(percentage <0.5, "red",
                      ifelse(percentage>=0.5 & percentage<0.8, "orange","green")),
         label=paste0(percentage *100, "%"),
         title = Province,
         Province = stringr::str_replace_all(string=Province, pattern=" ", repl="")
         ) %>%
        select(variable = Province, percentage, group, label , title )


overall_prog_1 <- paste0("Overall Progress: ", round(mean(Overall_progress_prov_graphs$percentage) * 100, 2) ,"%")

# Overall progress non head of hosehold

Overall_progress_gender <- gendert_tracking_merged %>%
  group_by(Province) %>%
  summarise(Target = sum(Target),
            Accepted = sum(Accepted, na.rm = T))


# # Overall progress %
overall_prog <-  paste0("Overall Progress: ",round((sum(Overall_progress_gender$Accepted, na.rm = T) / sum(Overall_progress_gender$Target, na.rm = T)) * 100, 2), "%")
  
# # province grapho gender
Overall_progress_prov_graphs_gender <- Overall_progress_gender %>%
  mutate(percentage =  round((Accepted / Target), digits = 3),
         percentage = case_when(
           percentage >= 1 ~ 1,
           TRUE ~ percentage
         ),
         group=ifelse(percentage <0.5, "red",
                      ifelse(percentage>=0.5 & percentage<0.8, "orange","green")),
         label=paste0(percentage *100, "%"),
         title = Province,
         Province = stringr::str_replace_all(string=Province, pattern=" ", repl="")
         ) %>%
        select(variable = Province, percentage, group, label , title )




# ########################################################################################
# 
# Enumerator productivity

enumerator_productivity <- data %>%
  group_by(Date = today, Enumerator = enumerator_uuid) %>%
  summarise(Interviews = n())

enumerator_productivity_many <- enumerator_productivity %>%
  filter(Interviews > max_interv)

enumerator_productivity_less <- enumerator_productivity %>%
  filter(Interviews < 4)

enumerator_productivity_final <- rbind(enumerator_productivity_many, enumerator_productivity_less) %>% arrange(desc(Date))


# Enumerator per survey status

enumer_per_survey_status <- data %>%
  group_by(Date = today, Enumerator = enumerator_uuid) %>%
  summarise(Accepted = sum(validity == "valid", na.rm = T),
            Deleted = sum(validity == "deleted", na.rm = T )
  ) %>% arrange(desc(Date))

# Survey status per day
survey_status_per_day <- data %>%
  group_by(Date = today) %>%
  summarise(Accepted = sum(validity == "valid", na.rm = T),
            Deleted = sum(validity == "deleted", na.rm = T )
  ) %>% arrange(desc(Date))

# survey lenght by enumerator

survey_lenght <- data %>%
  group_by(Enumerator = enumerator_uuid) %>%
  summarise(
    Average_duration = round(mean(interview_duration, na.rm = T),0)
  )

overall_survey_mean <- round(mean(as.numeric(data$interview_duration), na.rm = T),0)

survey_lenght$Overall_average <-  overall_survey_mean

# Enumerator with short interv duration
short_interviews_by_enum <- data %>%
  filter(interview_duration < time_limit) %>%
  select(Date = today,
         Enumerator = enumerator_uuid,
         Province = province,
         District = district,
         Settlment = village_eng,
         Duration =  interview_duration
  ) %>% mutate(
    Duration = round(Duration,0)
  ) %>% arrange(desc(Date))

# surveys done before start date
started_before <- data %>% 
  filter(today < assessment_start_date) %>% 
  select(Date = today,
         Enumerator = enumerator_uuid,
         Province = province,
         District = district,
         Settlement = village_eng)

# Average Flag by enumerator
average_flags_df <- data %>% 
  group_by(Enumerator = enumerator_uuid) %>%
  summarise(`Average Flags` = round(mean(sum_checks), 1))

# deletion
deletion_summary <- data %>% 
  group_by(province) %>% 
  summarise(
    Valid = sum(validity == "valid"),
    Deleted = sum(validity == "deleted"),
    Deletion_ratio = round(Deleted / n() * 100,1),
    Too_Short = sum(deletion_criteria_time == "Check", na.rm = T),
    # Too_Short_ratio = round(Too_Short / n() * 100,1),
    FCS = sum(deletion_criteria_low_FCS_score == "Check", na.rm = T),
    # FCS_ratio = round(FCS / n() * 100,2),
    Too_long = sum(deletion_criteria_long_interview == "Check", na.rm = T),
    # Too_long_ratio = round(Too_long / n() * 100,1),
    Too_many_flags = sum(deletion_criteria_6_flags == "Check", na.rm = T),
    # Too_many_flags_ratio = round(Too_many_flags / n() * 100,1),
    Wrong_population = sum(deletion_criteria_wrong_population == "Check", na.rm = T),
    Other = sum(!is.na(other_deletions), na.rm = T)
    # Wrong_population_ratio = round(Wrong_population / n() * 100,1)
    
  )
deletion_summary$province <-stringr::str_to_sentence(deletion_summary$province )

```


# {.tabset}

## Overall Progress
<center><h2> `r overall_prog_1`  </h2></center>

***

<center>**National, Population Groups Tracker**</center> </br>
```{r eval=TRUE, echo=FALSE, results='asis'}
kable(national_tracking_merged, col.names = c("Population Group","Target","Received",
                           "Accepted", "Deleted", "Deletion Rate", "Progress", "Remaining"), align=rep('l', 5))%>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F) %>% 
   column_spec(4, color = "green") %>%
   column_spec(5, color = "red") %>%
   column_spec(6, color = "red") %>%
   column_spec(7, color = "green") %>% 
   column_spec(8, bold = T)
  
```

***

<center>**Province Progress**</center> </br>
```{r eval=TRUE, echo=FALSE, results='asis' , fig.width=12,fig.height=12}

ggplot(Overall_progress_prov_graphs, aes(fill = group, ymax = percentage, ymin = 0, xmax = 2, xmin = 1)) +
  geom_rect(aes(ymax=1, ymin=0, xmax=2, xmin=1), fill ="#d1d3d4") +
  geom_rect() +
  coord_polar(theta = "y",start=-pi/2) + xlim(c(0, 2)) + ylim(c(0,2)) +
  geom_text(aes(x = 0, y = 0, label = label), size=5, family="Poppins SemiBold") +
  geom_text(aes(x=0.5, y=1.5, label=title), family="Poppins Light", size=4.2) +
  facet_wrap(~title, ncol = 6) +
  theme_void() +
  scale_fill_manual(values = c("red"="#ee5859", "orange"="#ff9933", "green"="#5B8930")) +
  scale_colour_manual(values = c("red"="#C9146C", "orange"="#DA9112", "green"="#129188")) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank()) +
  guides(fill=FALSE) +
  guides(colour=FALSE)



```


***


## Tracking - Province

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(province_tracking_merged, extensions = c('Buttons','RowGroup'),
              colnames=c("Province", "Population Group", "Target", "Received", "Accepted", "Deleted", "Deletion Rate", "Progress", "Remaining"),
              options = list(
                  pageLength = 200,
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                  columnDefs = list(list(className = 'dt-center', targets = 3:9)),
                  rowGroup = list(dataSrc = 1)
                )
              
              )  %>% 
  formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>%
  formatStyle('Deletion_Rate',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('perc_complete',  color = 'green', fontWeight = 'bold') %>%
  formatStyle('Remaining', fontWeight = 'bold')
```

***

## Tracking - District

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(district_tracking_merged, extensions = c('Buttons','RowGroup'),
              colnames=c("Province", "District", "Population Group", "Target", "Received", "Accepted", "Deleted", "Deletion Rate", "Progress", "Remaining"),
              options = list(
                  pageLength = 400,
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                  columnDefs = list(list(className = 'dt-center', targets = 4:9)),
                  rowGroup = list(dataSrc = 1)
                )
              
              )  %>% 
  formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>%
  formatStyle('Deletion_Rate',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('perc_complete',  color = 'green', fontWeight = 'bold') %>%
  formatStyle('Remaining', fontWeight = 'bold')
```

***

## Wrong Districts
<center>**Interviews Done in Wrong Districts**</center> </br>
```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(district_wrong_pop_merged, extensions = c('Buttons','RowGroup'),
              colnames=c("Province", "District", "Population Group", "Target", "Received", "Accepted", "Deleted", "Deletion Rate", "Progress", "Remaining"),
              options = list(
                  pageLength = 400,
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                  columnDefs = list(list(className = 'dt-center', targets = 4:9)),
                  rowGroup = list(dataSrc = 1)
                )
              
              )  %>% 
  formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('Accepted',  color = 'green', fontWeight = 'bold') %>%
  formatStyle('Deletion_Rate',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('perc_complete',  color = 'green', fontWeight = 'bold') %>%
  formatStyle('Remaining', fontWeight = 'bold')
```

***


## Tracking - Gender  

<center>**Gender Interview Tracker**</center> </br> 


```{r eval=TRUE, echo=FALSE, results='asis'}
kable(gendert_tracking_merged, col.names = c("Province","Target","Received",
                           "Accepted", "Deleted", "Deletion Rate", "Progress", "Remaining"), align=rep('l', 5)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F) %>% 
  column_spec(4, color = "green") %>%
  column_spec(5, color = "red") %>%
  column_spec(6, color = "red") %>%
  column_spec(7, color = "green") %>%
  column_spec(8, bold = T) 
  
ggplot(Overall_progress_prov_graphs_gender, aes(fill = group, ymax = percentage, ymin = 0, xmax = 2, xmin = 1)) +
  geom_rect(aes(ymax=1, ymin=0, xmax=2, xmin=1), fill ="#d1d3d4") +
  geom_rect() +
  coord_polar(theta = "y",start=-pi/2) + xlim(c(0, 2)) + ylim(c(0,2)) +
  geom_text(aes(x = 0, y = 0, label = label), size=4, family="Poppins SemiBold") +
  geom_text(aes(x=0.5, y=1.5, label=title), family="Poppins Light", size=4) +
  facet_wrap(~title, ncol = 4) +
  theme_void() +
  scale_fill_manual(values = c("red"="#ee5859", "orange"="#ff9933", "green"="#5B8930")) +
  scale_colour_manual(values = c("red"="#C9146C", "orange"="#DA9112", "green"="#129188")) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank()) +
  guides(fill=FALSE) +
  guides(colour=FALSE)


```


***

## General Checks  

<center>**Surveys made before the first day of data collection (**`r assessment_start_date`**)**</center> </br> 

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(started_before)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***

<center>**Enumerators who made a survey below 30 minutes** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(short_interviews_by_enum)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***

<center>**Number of survey per day of data collection** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_status_per_day)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***

<center>**Surveyors with very low or high productivity** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(enumerator_productivity_final)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***



<center>**Average Flags by Enumerator** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(average_flags_df)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***


<center>**Average interview duration by enumerator** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_lenght)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***

## Enumerator Progress


```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(enumer_per_survey_status ,extensions = 'Buttons',
              options = list(
                  buttons = c('csv', 'excel', 'pdf'),
                  columnDefs = list(list(className = 'dt-center', targets = 3:4)),
                  pageLength = 100,
                  dom = 'Bfrtip'
                )
  ) %>%
  formatStyle('Deleted',  color = 'red', fontWeight = 'bold') %>%
  formatStyle('Accepted',  color = 'green', fontWeight = 'bold')

```

***

## Deletion Summary

```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(deletion_summary ,extensions = 'Buttons',
               colnames = c("Province","Valid","Deleted",
                           "Deletion Rate", "Short Interviews", "Low FCS", "Long Interviews", "Too many Flags", "Wrong Pop", "Other"),
              options = list(
                  buttons = c('csv', 'excel', 'pdf'),
                  columnDefs = list(list(className = 'dt-center', targets = 2:9)),
                  pageLength = 100,
                  dom = 'Bfrtip'
                )
  ) 

```

***



